Modelling the innovation and extinction of archaeological ideas

### 2018-03-17 analysis/paper/citation-clusters/How-to-cluster-citations.Rmd
sketch of using citation communities

```{r}
length(unique(xx$.out))
```

@@

@@

```{r, eval=TRUE}
source(paste0(here::here(), "/pyrate_mcmc_logs/lineage_pyrate_data_0_BD_marginal_rates_RTT.r"))

>>>>

```{r}
# If we are resuming the analysis we can just start from here, and read in the data
# frame of citations.
xx <- readRDS( paste0(here::here(), "/analysis/data/derived_data/items_wth_refs.rds"))
length(unique(xx$.out))
```

@@

```{r, eval=F}

@@

```{r, eval=F}
source(paste0(here::here(), "/pyrate_mcmc_logs/lineage_pyrate_data_0_BD_marginal_rates_RTT.r"))
